---
title: "Homework 3"
author: "Tyler Echols"
date: "6/13/2022"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
subtitle: 4375 Machine Learning with Dr. Mazidi
---

This homework runs logistic regression to predict the binary feature of whether or not a person was admitted to graduate school, based on a set of predictors: GRE score, TOEFL score, rating of undergrad university attended, SOP statement of purpose, LOR letter or recommendation, Undergrad GPA, Research experience (binary).

The data set was downloaded from Kaggle: https://www.kaggle.com/mohansacharya/graduate-admissions

The data is available in Piazza. 

## Step 1 Load the data

* Load the data
* Examine the first few rows with head()

```{r}
# your code here
df <- read.csv("Admission_Predict.csv", header = TRUE)
head(df)
```

## Step 2 Data Wrangling

Perform the following steps:

* Make Research a factor
* Get rid of the Serial No column
* Make a new column that is binary factor based on if Chance.of.Admit > 0.5. Hint: See p. 40 in the book. 
* Output column names with names() function
* Output a summary of the data
* Is the data set unbalanced? Why or why not?

 Your commentary here: It looks balanced because on each graph because it seems you to be sharing the same information. 

```{r}
# your code here
df$Research <- factor(df$Research)
df$Serial.No. <- NULL
head(df)
df$bFactor <- ifelse(df$Chance.of.Admit > 0.5, 1, 0)
head(df)
names(df)
```

```{r}
# put the summary here
summary(df)
```

## Step 3 Data Visualization

* Create a side-by-side graph with Admit on the x axis of both graphs, GRE score on the y axis of one graph and TOEFL score on the y axis of the other graph; save/restore the original graph parameters
* Comment on the graphs and what they are telling you about whether GRE and TOEFL are good predictors
* You will get a lot of warnings, you can suppress them with disabling warnings as shown below:

```
{r,warning=FALSE}
```

Your commentary here: Both graph's are going up at an gradualling increasing pace. 

```{r,warning=FALSE}
# your code here
plot(df$Chance.of.Admit, df$GRE.Score)
plot(df$Chance.of.Admit, df$TOEFL.Score)
```


## Step 4 Divide train/test

* Divide into 75/25 train/test, using seed 1234

```{r}
# your code here
set.seed(1234)
sample <- sample.int(n=nrow(df), size=floor(.75*nrow(df)), replace = F)
train = df[sample,]
test = df[-sample,] 
```

## Step 5 Build a Model with all predictors 

* Build a model, predicting Admit from all predictors
* Output a summary of the model
* Did you get an error? Why? Hint: see p. 120 Warning

Your commentary here: the error are got are talking about how they can not fit between the numerically set values  

```{r}
# your code here
glm1 <- glm(bFactor~., family=binomial,data=train)
summary(glm1)
```

## Step 6 Build a Model with all predictors except Chance.of.Admit

* Build another model, predicting Admit from all predictors *except* Chance.of.Admit
* Output a summary of the model
* Did you get an error? Why or why not?
# There were no error's for this because It has a more defined bound to work with 

```{r}
# your code here
glm2 <- glm(bFactor~. -Chance.of.Admit , family=binomial,data=train)
summary(glm2)
```

## Step 7 Predict probabilities

* Predict the probabilities using type="response"
* Examine a few probabilities and the corresponding Chance.of.Admit values
* Run cor() on the predicted probs and the Chance.of.Admit, and output the correlation
* What do you conclude from this correlation. 

Your commentary here:that these probabilities are still in the middle of 0 and 1. 

```{r}
# your code here
probs <- predict(glm2, newdata=df, type="response")
head(probs)
cor(probs,df$Chance.of.Admit)
```

## Step 8 Make binary predictions, print table and accuracy

* Now make binary predictions
* Output a table comparing the predictions and the binary Admit column
* Calculate and output accuracy
* Was the model able to generalize well to new data?

Your commentary here:The model only repeated new data that was already presented. 

```{r}
# your code here
glm2 <- glm(bFactor~., family=binomial,data=train)
probs <- predict(glm2,  newdata=test, type="response")
pred <- ifelse(probs> 0.5, 2, 1)
acc <- mean(pred == as.integer(test$bFactor))
summary(glm2)
```

## Step 9 Output ROCR and AUC

* Output a ROCR graph
* Extract and output the AUC metric

```{r}
# your code here
##library(ROCR)
##rocNew <- roc(df$Chance.of.Admit, glm2$fitted.values, plot = TRUE)
##rocNew
##cat("Area under the curve: ", rocNew$auc)

```


## Step 10

* Make two more graphs and comment on what you learned from each graph:
  * Admit on x axis, SOP on y axis
  * Research on x axis, SOP on y axis
  
Your commentary here: Both graphic have very low predictors and and random variables. 


```{r}
# plot 1
plot( x = df$Chance.of.Admit, y = df$SOP, main = "Admisson VS. SOP", ylab = "SOP", xlab = "Chance of Admissions")
```

```{r}
# plot 2
plot (x = df$Research, y = df$SOP, main = "Research and SOP", ylab = "SOP", xlab = "Research")
```

